---
title: "R Notebook"
output: html_notebook
---

```{r}
set.seed(313549)
library(microbenchmark)

```

# Box-Müller algorithm

```{r}
box_muller <- function(n, niu = 0, sigma = 1)
{
  stopifnot(sigma > 0)
  stopifnot(is.numeric(niu))
  stopifnot(length(n) == 1)
  
  u1 <- runif(n, 0, 1)
  u2 <- runif(n, 0, 1)
  
  z1 <- sqrt(-2*log(u1))*cos(2*pi*u2)
  z2 <- sqrt(-2*log(u1))*sin(2*pi*u2)
  
  normal1 <- niu + sigma*z1
  normal2 <- niu + sigma*z2
  
  normal <- c(normal1, normal2)
  
  return(normal)
}

```

# Box-Müller algorithm for one variable

```{r}
box_muller_one_variable <- function(n, niu = 0, sigma = 1)
{
  stopifnot(sigma > 0)
  stopifnot(is.numeric(niu))
  stopifnot(length(n) == 1)
  
  y1 <- rexp(n, 1)
  y2 <- rexp(n, 1)
  
  accept <- ((1-y1)**2)/2 < y2
  y1 <- y1[accept]
  
  u <- runif(length(y1), 0, 1)
  u <- 2*u - 1
  u <- sapply(u, sign)
  y1 <- y1*u

  y1 <- sigma*y1 + niu
  
  return(y1)
}

```

# Acceptance-rejection method

```{r}
acceptance_rejection <- function(n, niu = 0, sigma = 1)
{
  stopifnot(sigma > 0)
  stopifnot(is.numeric(niu))
  stopifnot(length(n) == 1)
  
  u1 <- runif(n, 0, 1)
  y <- rexp(n, 1)
  
  accept <- sqrt(exp(1))*u1*exp(-y) <= exp((-y**2)/2)
  x <- y[accept]
  
  u2 <- runif(length(x), 0, 1)
  u2 <- 2*u2 - 1
  u2 <- sapply(u2, sign)
  x <- x*u2
  
  x <- sigma*x + niu
  
  return(x)
}

```

# Marsaglia-Bray algorithm

```{r}
marsaglia <- function(n, niu = 0, sigma = 1)
{
  stopifnot(sigma > 0)
  stopifnot(is.numeric(niu))
  stopifnot(length(n) == 1)
  
  u1 <- runif(n, 0, 1)
  u2 <- runif(n, 0, 1)
  
  u1 <- 2*u1 - 1
  u2 <- 2*u2 - 1
  
  r <- sqrt(u1**2 + u2**2)
  accept <- u1**2 + u2**2 <= 1
  
  r <- r[accept]
  
  z1 <- sqrt(-2*log(r**2))*u1[accept]/r
  z2 <- sqrt(-2*log(r**2))*u2[accept]/r
  
  normal1 <- niu + sigma*z1
  normal2 <- niu + sigma*z2
  
  normal <- c(normal1, normal2)
  
  return(normal)
}

```

# Results for one variable generated from each algorithm (for n = 1000)

```{r}
# Generating variables from each algorithm
bm <- box_muller(1000, 0, 1)
bmov <- box_muller_one_variable(1000, 0, 1)
ar <- acceptance_rejection(1000, 0, 1)
mb <- marsaglia(1000, 0, 1)

# Getting two independent variables returned from Box-Müller and Marsaglia-Bray algorithms
bm1 <- bm[1:(length(bm)/2)]
bm2 <- bm[((length(bm)/2)+1):(length(bm))]
mb1 <- mb[1:(length(mb)/2)]
mb2 <- mb[((length(mb)/2)+1):(length(mb))]

# First 100 values received using each algorithm
print("Box_Müller X1:")
head(bm1, 100L)
print("Box_Müller X2:")
head(bm2, 100L)
print("Box_Müller_one_variable:")
head(bmov, 100L)
print("Acceptance_Rejection:")
head(ar, 100L)
print("Marsaglia X1:")
head(mb1, 100L)
print("Marsaglia X2:")
head(mb2, 100L)

```

```{r}
# Number of received values
print(paste("Length of Box_Muller X1:", length(bm1)))
print(paste("Length of Box_Muller X2:", length(bm2)))
print(paste("Length of Box_Muller_one_variable:", length(bmov)))
print(paste("Length of Acceptance_Rejection:", length(ar)))
print(paste("Length of Marsaglia X1:", length(mb1)))
print(paste("Length of Marsaglia X2:", length(mb2)))

```

```{r}
# Kolmogorov-Smirnov test: variables are distributed from normal distribution vs they are not
ks.test(bm1, rnorm(length(bm1), 0, 1))
ks.test(bm2, rnorm(length(bm2), 0, 1))
ks.test(bmov, rnorm(length(bmov), 0, 1))
ks.test(ar, rnorm(length(ar), 0, 1))
ks.test(mb1, rnorm(length(mb1), 0, 1))
ks.test(mb2, rnorm(length(mb2), 0, 1))

```

```{r}
# Shapiro-Wilk test: variables are distributed from normal distribution vs they are not
shapiro.test(bm1)
shapiro.test(bm2)
shapiro.test(bmov)
shapiro.test(ar)
shapiro.test(mb1)
shapiro.test(mb2)

```

```{r}
# QQ-plots for each variable in order to verify if they are normally distributed
qqnorm(bm1, main = "Box-Müller X1")
qqline(bm1, col="red")

qqnorm(bm2, main = "Box-Müller X2")
qqline(bm2, col="red")

qqnorm(bmov, main = "Box-Müller one variable")
qqline(bmov, col="red")

qqnorm(ar, main = "Acceptance-Rejection")
qqline(ar, col="red")

qqnorm(mb1, main = "Marsaglia X1")
qqline(mb1, col="red")

qqnorm(mb2, main = "Marsaglia X2")
qqline(mb2, col="red")

```

# Experimental part - verifying algorithms using 100 samples received from each algorithm

```{r}
# In lists tested parameters will be kept
bm1MeanLength100 <- list()
bm2MeanLength100 <- list()
bmovMeanLength100 <- list()
arMeanLength100 <- list()
mb1MeanLength100 <- list()
mb2MeanLength100 <- list()

bm1MeanKS100 <- list()
bm2MeanKS100 <- list()
bmovMeanKS100 <- list()
arMeanKS100 <- list()
mb1MeanKS100 <- list()
mb2MeanKS100 <- list()

bm1MeanShapiro100 <- list()
bm2MeanShapiro100 <- list()
bmovMeanShapiro100 <- list()
arMeanShapiro100 <- list()
mb1MeanShapiro100 <- list()
mb2MeanShapiro100 <- list()

bm1MeanLength1000 <- list()
bm2MeanLength1000 <- list()
bmovMeanLength1000 <- list()
arMeanLength1000 <- list()
mb1MeanLength1000 <- list()
mb2MeanLength1000 <- list()

bm1MeanKS1000 <- list()
bm2MeanKS1000 <- list()
bmovMeanKS1000 <- list()
arMeanKS1000 <- list()
mb1MeanKS1000 <- list()
mb2MeanKS1000 <- list()

bm1MeanShapiro1000 <- list()
bm2MeanShapiro1000 <- list()
bmovMeanShapiro1000 <- list()
arMeanShapiro1000 <- list()
mb1MeanShapiro1000 <- list()
mb2MeanShapiro1000 <- list()

bm1MeanLength10000 <- list()
bm2MeanLength10000 <- list()
bmovMeanLength10000 <- list()
arMeanLength10000 <- list()
mb1MeanLength10000 <- list()
mb2MeanLength10000 <- list()

bm1MeanKS10000 <- list()
bm2MeanKS10000 <- list()
bmovMeanKS10000 <- list()
arMeanKS10000 <- list()
mb1MeanKS10000 <- list()
mb2MeanKS10000 <- list()

bm1MeanLength100000 <- list()
bm2MeanLength100000 <- list()
bmovMeanLength100000 <- list()
arMeanLength100000 <- list()
mb1MeanLength100000 <- list()
mb2MeanLength100000 <- list()

bm1MeanKS100000 <- list()
bm2MeanKS100000 <- list()
bmovMeanKS100000 <- list()
arMeanKS100000 <- list()
mb1MeanKS100000 <- list()
mb2MeanKS100000 <- list()

```

# For n = 100 (generating max 100 values)

```{r}
for (i in 1:100)
{
  # Generating variables from each algorithm
  bm <- box_muller(100, 0, 1)
  bmov <- box_muller_one_variable(100, 0, 1)
  ar <- acceptance_rejection(100, 0, 1)
  mb <- marsaglia(100, 0, 1)

  # Getting two independent variables returned from Box-Müller and Marsaglia-Bray algorithms
  bm1 <- bm[1:(length(bm)/2)]
  bm2 <- bm[((length(bm)/2)+1):(length(bm))]
  mb1 <- mb[1:(length(mb)/2)]
  mb2 <- mb[((length(mb)/2)+1):(length(mb))]
  
  # Getting numbers of values
  bm1MeanLength100[i] <- length(bm1)
  bm2MeanLength100[i] <- length(bm2)
  bmovMeanLength100[i] <- length(bmov)
  arMeanLength100[i] <- length(ar)
  mb1MeanLength100[i] <- length(mb1)
  mb2MeanLength100[i] <- length(mb2)
  
  # Getting p-values using Kolmogorov-Smirnov test: variables are distributed from normal distribution vs they are not
  bm1MeanKS100[i] <- ks.test(bm1, rnorm(length(bm1), 0, 1))$p.value
  bm2MeanKS100[i] <- ks.test(bm2, rnorm(length(bm2), 0, 1))$p.value
  bmovMeanKS100[i] <- ks.test(bmov, rnorm(length(bmov), 0, 1))$p.value
  arMeanKS100[i] <- ks.test(ar, rnorm(length(ar), 0, 1))$p.value
  mb1MeanKS100[i] <- ks.test(mb1, rnorm(length(mb1), 0, 1))$p.value
  mb2MeanKS100[i] <- ks.test(mb2, rnorm(length(mb2), 0, 1))$p.value
  
  # Getting p-values using Shapiro-Wilk test: variables are distributed from normal distribution vs they are not
  bm1MeanShapiro100[i] <- shapiro.test(bm1)$p.value
  bm2MeanShapiro100[i] <- shapiro.test(bm2)$p.value
  bmovMeanShapiro100[i] <- shapiro.test(bmov)$p.value
  arMeanShapiro100[i] <- shapiro.test(ar)$p.value
  mb1MeanShapiro100[i] <- shapiro.test(mb1)$p.value
  mb2MeanShapiro100[i] <- shapiro.test(mb2)$p.value
}

```

# For n = 1000 (generating max 1000 values)

```{r}
for (i in 1:100)
{
  # Generating variables from each algorithm
  bm <- box_muller(1000, 0, 1)
  bmov <- box_muller_one_variable(1000, 0, 1)
  ar <- acceptance_rejection(1000, 0, 1)
  mb <- marsaglia(1000, 0, 1)

  # Getting two independent variables returned from Box-Müller and Marsaglia-Bray algorithms
  bm1 <- bm[1:(length(bm)/2)]
  bm2 <- bm[((length(bm)/2)+1):(length(bm))]
  mb1 <- mb[1:(length(mb)/2)]
  mb2 <- mb[((length(mb)/2)+1):(length(mb))]
  
  # Getting numbers of values
  bm1MeanLength1000[i] <- length(bm1)
  bm2MeanLength1000[i] <- length(bm2)
  bmovMeanLength1000[i] <- length(bmov)
  arMeanLength1000[i] <- length(ar)
  mb1MeanLength1000[i] <- length(mb1)
  mb2MeanLength1000[i] <- length(mb2)
  # Getting p-values using Kolmogorov-Smirnov test: variables are distributed from normal distribution vs they are not
  bm1MeanKS1000[i] <- ks.test(bm1, rnorm(length(bm1), 0, 1))$p.value
  bm2MeanKS1000[i] <- ks.test(bm2, rnorm(length(bm2), 0, 1))$p.value
  bmovMeanKS1000[i] <- ks.test(bmov, rnorm(length(bmov), 0, 1))$p.value
  arMeanKS1000[i] <- ks.test(ar, rnorm(length(ar), 0, 1))$p.value
  mb1MeanKS1000[i] <- ks.test(mb1, rnorm(length(mb1), 0, 1))$p.value
  mb2MeanKS1000[i] <- ks.test(mb2, rnorm(length(mb2), 0, 1))$p.value
  
  # Getting p-values using Shapiro-Wilk test: variables are distributed from normal distribution vs they are not
  bm1MeanShapiro1000[i] <- shapiro.test(bm1)$p.value
  bm2MeanShapiro1000[i] <- shapiro.test(bm2)$p.value
  bmovMeanShapiro1000[i] <- shapiro.test(bmov)$p.value
  arMeanShapiro1000[i] <- shapiro.test(ar)$p.value
  mb1MeanShapiro1000[i] <- shapiro.test(mb1)$p.value
  mb2MeanShapiro1000[i] <- shapiro.test(mb2)$p.value
}

```

# For n = 10000 (generating max 10000 values)

```{r}
for (i in 1:100)
{
  # Generating variables from each algorithm
  bm <- box_muller(10000, 0, 1)
  bmov <- box_muller_one_variable(10000, 0, 1)
  ar <- acceptance_rejection(10000, 0, 1)
  mb <- marsaglia(10000, 0, 1)

  # Getting two independent variables returned from Box-Müller and Marsaglia-Bray algorithms
  bm1 <- bm[1:(length(bm)/2)]
  bm2 <- bm[((length(bm)/2)+1):(length(bm))]
  mb1 <- mb[1:(length(mb)/2)]
  mb2 <- mb[((length(mb)/2)+1):(length(mb))]
  
  # Getting numbers of values
  bm1MeanLength10000[i] <- length(bm1)
  bm2MeanLength10000[i] <- length(bm2)
  bmovMeanLength10000[i] <- length(bmov)
  arMeanLength10000[i] <- length(ar)
  mb1MeanLength10000[i] <- length(mb1)
  mb2MeanLength10000[i] <- length(mb2)
  
  # Getting p-values using Kolmogorov-Smirnov test: variables are distributed from normal distribution vs they are not
  bm1MeanKS10000[i] <- ks.test(bm1, rnorm(length(bm1), 0, 1))$p.value
  bm2MeanKS10000[i] <- ks.test(bm2, rnorm(length(bm2), 0, 1))$p.value
  bmovMeanKS10000[i] <- ks.test(bmov, rnorm(length(bmov), 0, 1))$p.value
  arMeanKS10000[i] <- ks.test(ar, rnorm(length(ar), 0, 1))$p.value
  mb1MeanKS10000[i] <- ks.test(mb1, rnorm(length(mb1), 0, 1))$p.value
  mb2MeanKS10000[i] <- ks.test(mb2, rnorm(length(mb2), 0, 1))$p.value
}

```

# For n = 100000 (generating max 100000 values)

```{r}
for (i in 1:100)
{
  # Generating variables from each algorithm
  bm <- box_muller(100000, 0, 1)
  bmov <- box_muller_one_variable(100000, 0, 1)
  ar <- acceptance_rejection(100000, 0, 1)
  mb <- marsaglia(100000, 0, 1)

  # Getting two independent variables returned from Box-Müller and Marsaglia-Bray algorithms
  bm1 <- bm[1:(length(bm)/2)]
  bm2 <- bm[((length(bm)/2)+1):(length(bm))]
  mb1 <- mb[1:(length(mb)/2)]
  mb2 <- mb[((length(mb)/2)+1):(length(mb))]
  
  # Getting numbers of values
  bm1MeanLength100000[i] <- length(bm1)
  bm2MeanLength100000[i] <- length(bm2)
  bmovMeanLength100000[i] <- length(bmov)
  arMeanLength100000[i] <- length(ar)
  mb1MeanLength100000[i] <- length(mb1)
  mb2MeanLength100000[i] <- length(mb2)
  
  # Getting p-values using Kolmogorov-Smirnov test: variables are distributed from normal distribution vs they are not
  bm1MeanKS100000[i] <- ks.test(bm1, rnorm(length(bm1), 0, 1))$p.value
  bm2MeanKS100000[i] <- ks.test(bm2, rnorm(length(bm2), 0, 1))$p.value
  bmovMeanKS100000[i] <- ks.test(bmov, rnorm(length(bmov), 0, 1))$p.value
  arMeanKS100000[i] <- ks.test(ar, rnorm(length(ar), 0, 1))$p.value
  mb1MeanKS100000[i] <- ks.test(mb1, rnorm(length(mb1), 0, 1))$p.value
  mb2MeanKS100000[i] <- ks.test(mb2, rnorm(length(mb2), 0, 1))$p.value
}

```

# Mean values of parameters

```{r}
# Mean Numbers of values for n = 100
print(paste("bm1MeanLength100: ", mean(sapply(bm1MeanLength100, mean))))
print(paste("bm2MeanLength100: ", mean(sapply(bm2MeanLength100, mean))))
print(paste("bmovMeanLength100: ", mean(sapply(bmovMeanLength100, mean))))
print(paste("arMeanLength100: ", mean(sapply(arMeanLength100, mean))))
print(paste("mb1MeanLength100: ", mean(sapply(mb1MeanLength100, mean))))
print(paste("mb2MeanLength100: ", mean(sapply(mb2MeanLength100, mean))))

# Mean p-values using Kolmogorov-Smirnov test for n = 100
print(paste("bm1MeanKS100: ", mean(sapply(bm1MeanKS100, mean))))
print(paste("bm2MeanKS100: ", mean(sapply(bm2MeanKS100, mean))))
print(paste("bmovMeanKS100: ", mean(sapply(bmovMeanKS100, mean))))
print(paste("arMeanKS100: ", mean(sapply(arMeanKS100, mean))))
print(paste("mb1MeanKS100: ", mean(sapply(mb1MeanKS100, mean))))
print(paste("mb2MeanKS100: ", mean(sapply(mb2MeanKS100, mean))))

# Mean p-values using Shapiro-Wilk test for n = 100
print(paste("bm1MeanShapiro100: ", mean(sapply(bm1MeanShapiro100, mean))))
print(paste("bm2MeanShapiro100: ", mean(sapply(bm2MeanShapiro100, mean))))
print(paste("bmovMeanShapiro100: ", mean(sapply(bmovMeanShapiro100, mean))))
print(paste("arMeanShapiro100: ", mean(sapply(arMeanShapiro100, mean))))
print(paste("mb1MeanShapiro100: ", mean(sapply(mb1MeanShapiro100, mean))))
print(paste("mb2MeanShapiro100: ", mean(sapply(mb2MeanShapiro100, mean))))

# Mean Numbers of values for n = 1000
print(paste("bm1MeanLength1000: ", mean(sapply(bm1MeanLength1000, mean))))
print(paste("bm2MeanLength1000: ", mean(sapply(bm2MeanLength1000, mean))))
print(paste("bmovMeanLength1000: ", mean(sapply(bmovMeanLength1000, mean))))
print(paste("arMeanLength1000: ", mean(sapply(arMeanLength1000, mean))))
print(paste("mb1MeanLength1000: ", mean(sapply(mb1MeanLength1000, mean))))
print(paste("mb2MeanLength1000: ", mean(sapply(mb2MeanLength1000, mean))))

# Mean p-values using Kolmogorov-Smirnov test for n = 1000
print(paste("bm1MeanKS1000: ", mean(sapply(bm1MeanKS1000, mean))))
print(paste("bm2MeanKS1000: ", mean(sapply(bm2MeanKS1000, mean))))
print(paste("bmovMeanKS1000: ", mean(sapply(bmovMeanKS1000, mean))))
print(paste("arMeanKS1000: ", mean(sapply(arMeanKS1000, mean))))
print(paste("mb1MeanKS1000: ", mean(sapply(mb1MeanKS1000, mean))))
print(paste("mb2MeanKS1000: ", mean(sapply(mb2MeanKS1000, mean))))

# Mean p-values using Shapiro-Wilk test for n = 1000
print(paste("bm1MeanShapiro1000: ", mean(sapply(bm1MeanShapiro1000, mean))))
print(paste("bm2MeanShapiro1000: ", mean(sapply(bm2MeanShapiro1000, mean))))
print(paste("bmovMeanShapiro1000: ", mean(sapply(bmovMeanShapiro1000, mean))))
print(paste("arMeanShapiro1000: ", mean(sapply(arMeanShapiro1000, mean))))
print(paste("mb1MeanShapiro1000: ", mean(sapply(mb1MeanShapiro1000, mean))))
print(paste("mb2MeanShapiro1000: ", mean(sapply(mb2MeanShapiro1000, mean))))

# Mean Numbers of values for n = 10000
print(paste("bm1MeanLength10000: ", mean(sapply(bm1MeanLength10000, mean))))
print(paste("bm2MeanLength10000: ", mean(sapply(bm2MeanLength10000, mean))))
print(paste("bmovMeanLength10000: ", mean(sapply(bmovMeanLength10000, mean))))
print(paste("arMeanLength10000: ", mean(sapply(arMeanLength10000, mean))))
print(paste("mb1MeanLength10000: ", mean(sapply(mb1MeanLength10000, mean))))
print(paste("mb2MeanLength10000: ", mean(sapply(mb2MeanLength10000, mean))))

# Mean p-values using Kolmogorov-Smirnov test for n = 10000
print(paste("bm1MeanKS10000: ", mean(sapply(bm1MeanKS10000, mean))))
print(paste("bm2MeanKS10000: ", mean(sapply(bm2MeanKS10000, mean))))
print(paste("bmovMeanKS10000: ", mean(sapply(bmovMeanKS10000, mean))))
print(paste("arMeanKS10000: ", mean(sapply(arMeanKS10000, mean))))
print(paste("mb1MeanKS10000: ", mean(sapply(mb1MeanKS10000, mean))))
print(paste("mb2MeanKS10000: ", mean(sapply(mb2MeanKS10000, mean))))

# Mean Numbers of values for n = 100000
print(paste("bm1MeanLength100000: ", mean(sapply(bm1MeanLength100000, mean))))
print(paste("bm2MeanLength100000: ", mean(sapply(bm2MeanLength100000, mean))))
print(paste("bmovMeanLength100000: ", mean(sapply(bmovMeanLength100000, mean))))
print(paste("arMeanLength100000: ", mean(sapply(arMeanLength100000, mean))))
print(paste("mb1MeanLength100000: ", mean(sapply(mb1MeanLength100000, mean))))
print(paste("mb2MeanLength100000: ", mean(sapply(mb2MeanLength100000, mean))))

# Mean p-values using Kolmogorov-Smirnov test for n = 100000
print(paste("bm1MeanKS100000: ", mean(sapply(bm1MeanKS100000, mean))))
print(paste("bm2MeanKS100000: ", mean(sapply(bm2MeanKS100000, mean))))
print(paste("bmovMeanKS100000: ", mean(sapply(bmovMeanKS100000, mean))))
print(paste("arMeanKS100000: ", mean(sapply(arMeanKS100000, mean))))
print(paste("mb1MeanKS100000: ", mean(sapply(mb1MeanKS100000, mean))))
print(paste("mb2MeanKS100000: ", mean(sapply(mb2MeanKS100000, mean))))

```

# Time of computing for 100 iterations and n = 100

```{r}
microbenchmark(box_muller(100, 0, 1), 
               box_muller_one_variable(100, 0, 1),
               acceptance_rejection(100, 0, 1), 
               marsaglia(100, 0, 1))

```

# Time of computing for 100 iterations and n = 1000

```{r}
microbenchmark(box_muller(1000, 0, 1), 
               box_muller_one_variable(1000, 0, 1),
               acceptance_rejection(1000, 0, 1), 
               marsaglia(1000, 0, 1))

```

# Time of computing for 100 iterations and n = 10000

```{r}
microbenchmark(box_muller(10000, 0, 1), 
               box_muller_one_variable(10000, 0, 1),
               acceptance_rejection(10000, 0, 1), 
               marsaglia(10000, 0, 1))

```

# Time of computing for 100 iterations and n = 100000

```{r}
microbenchmark(box_muller(100000, 0, 1), 
               box_muller_one_variable(100000, 0, 1),
               acceptance_rejection(100000, 0, 1), 
               marsaglia(100000, 0, 1))

```

```{r}
# Number of p-values <= 0.05 using Kolmogorov-Smirnov test for n = 100
print(paste("bm1CountKS100: ", length((sapply(bm1MeanKS100, mean) <= 0.05)[(sapply(bm1MeanKS100, mean) <= 0.05) == TRUE])))
print(paste("bm2CountKS100: ", length((sapply(bm2MeanKS100, mean) <= 0.05)[(sapply(bm2MeanKS100, mean) <= 0.05) == TRUE])))
print(paste("bmovCountKS100: ", length((sapply(bmovMeanKS100, mean) <= 0.05)[(sapply(bmovMeanKS100, mean) <= 0.05) == TRUE])))
print(paste("arCountKS100: ", length((sapply(arMeanKS100, mean) <= 0.05)[(sapply(arMeanKS100, mean) <= 0.05) == TRUE])))
print(paste("mb1CountKS100: ", length((sapply(mb1MeanKS100, mean) <= 0.05)[(sapply(mb1MeanKS100, mean) <= 0.05) == TRUE])))
print(paste("mb2CountKS100: ", length((sapply(mb2MeanKS100, mean) <= 0.05)[(sapply(mb2MeanKS100, mean) <= 0.05) == TRUE])))

# Number of p-values <= 0.05 using Shapiro-Wilk test for n = 100
print(paste("bm1CountShapiro100: ", length((sapply(bm1MeanShapiro100, mean) <= 0.05)[(sapply(bm1MeanShapiro100, mean) <= 0.05) == TRUE])))
print(paste("bm2CountShapiro100: ", length((sapply(bm2MeanShapiro100, mean) <= 0.05)[(sapply(bm2MeanShapiro100, mean) <= 0.05) == TRUE])))
print(paste("bmovCountShapiro100: ", length((sapply(bmovMeanShapiro100, mean) <= 0.05)[(sapply(bmovMeanShapiro100, mean) <= 0.05) == TRUE])))
print(paste("arCountShapiro100: ", length((sapply(arMeanShapiro100, mean) <= 0.05)[(sapply(arMeanShapiro100, mean) <= 0.05) == TRUE])))
print(paste("mb1CountShapiro100: ", length((sapply(mb1MeanShapiro100, mean) <= 0.05)[(sapply(mb1MeanShapiro100, mean) <= 0.05) == TRUE])))
print(paste("mb2CountShapiro100: ", length((sapply(mb2MeanShapiro100, mean) <= 0.05)[(sapply(mb2MeanShapiro100, mean) <= 0.05) == TRUE])))

# Number of p-values <= 0.05 using Kolmogorov-Smirnov test for n = 1000
print(paste("bm1CountKS1000: ", length((sapply(bm1MeanKS1000, mean) <= 0.05)[(sapply(bm1MeanKS1000, mean) <= 0.05) == TRUE])))
print(paste("bm2CountKS1000: ", length((sapply(bm2MeanKS1000, mean) <= 0.05)[(sapply(bm2MeanKS1000, mean) <= 0.05) == TRUE])))
print(paste("bmovCountKS1000: ", length((sapply(bmovMeanKS1000, mean) <= 0.05)[(sapply(bmovMeanKS1000, mean) <= 0.05) == TRUE])))
print(paste("arCountKS1000: ", length((sapply(arMeanKS1000, mean) <= 0.05)[(sapply(arMeanKS1000, mean) <= 0.05) == TRUE])))
print(paste("mb1CountKS1000: ", length((sapply(mb1MeanKS1000, mean) <= 0.05)[(sapply(mb1MeanKS1000, mean) <= 0.05) == TRUE])))
print(paste("mb2CountKS1000: ", length((sapply(mb2MeanKS1000, mean) <= 0.05)[(sapply(mb2MeanKS1000, mean) <= 0.05) == TRUE])))

# Number of p-values <= 0.05 using Shapiro-Wilk test for n = 1000
print(paste("bm1CountShapiro1000: ", length((sapply(bm1MeanShapiro1000, mean) <= 0.05)[(sapply(bm1MeanShapiro1000, mean) <= 0.05) == TRUE])))
print(paste("bm2CountShapiro1000: ", length((sapply(bm2MeanShapiro1000, mean) <= 0.05)[(sapply(bm2MeanShapiro1000, mean) <= 0.05) == TRUE])))
print(paste("bmovCountShapiro1000: ", length((sapply(bmovMeanShapiro1000, mean) <= 0.05)[(sapply(bmovMeanShapiro1000, mean) <= 0.05) == TRUE])))
print(paste("arCountShapiro1000: ", length((sapply(arMeanShapiro1000, mean) <= 0.05)[(sapply(arMeanShapiro1000, mean) <= 0.05) == TRUE])))
print(paste("mb1CountShapiro1000: ", length((sapply(mb1MeanShapiro1000, mean) <= 0.05)[(sapply(mb1MeanShapiro1000, mean) <= 0.05) == TRUE])))
print(paste("mb2CountShapiro1000: ", length((sapply(mb2MeanShapiro1000, mean) <= 0.05)[(sapply(mb2MeanShapiro1000, mean) <= 0.05) == TRUE])))

# Number of p-values <= 0.05 using Kolmogorov-Smirnov test for n = 10000
print(paste("bm1CountKS10000: ", length((sapply(bm1MeanKS10000, mean) <= 0.05)[(sapply(bm1MeanKS10000, mean) <= 0.05) == TRUE])))
print(paste("bm2CountKS10000: ", length((sapply(bm2MeanKS10000, mean) <= 0.05)[(sapply(bm2MeanKS10000, mean) <= 0.05) == TRUE])))
print(paste("bmovCountKS10000: ", length((sapply(bmovMeanKS10000, mean) <= 0.05)[(sapply(bmovMeanKS10000, mean) <= 0.05) == TRUE])))
print(paste("arCountKS10000: ", length((sapply(arMeanKS10000, mean) <= 0.05)[(sapply(arMeanKS10000, mean) <= 0.05) == TRUE])))
print(paste("mb1CountKS10000: ", length((sapply(mb1MeanKS10000, mean) <= 0.05)[(sapply(mb1MeanKS10000, mean) <= 0.05) == TRUE])))
print(paste("mb2CountKS10000: ", length((sapply(mb2MeanKS10000, mean) <= 0.05)[(sapply(mb2MeanKS10000, mean) <= 0.05) == TRUE])))

# Number of p-values <= 0.05 using Kolmogorov-Smirnov test for n = 100000
print(paste("bm1CountKS100000: ", length((sapply(bm1MeanKS100000, mean) <= 0.05)[(sapply(bm1MeanKS100000, mean) <= 0.05) == TRUE])))
print(paste("bm2CountKS100000: ", length((sapply(bm2MeanKS100000, mean) <= 0.05)[(sapply(bm2MeanKS100000, mean) <= 0.05) == TRUE])))
print(paste("bmovCountKS100000: ", length((sapply(bmovMeanKS100000, mean) <= 0.05)[(sapply(bmovMeanKS100000, mean) <= 0.05) == TRUE])))
print(paste("arCountKS100000: ", length((sapply(arMeanKS100000, mean) <= 0.05)[(sapply(arMeanKS100000, mean) <= 0.05) == TRUE])))
print(paste("mb1CountKS100000: ", length((sapply(mb1MeanKS100000, mean) <= 0.05)[(sapply(mb1MeanKS100000, mean) <= 0.05) == TRUE])))
print(paste("mb2CountKS100000: ", length((sapply(mb2MeanKS100000, mean) <= 0.05)[(sapply(mb2MeanKS100000, mean) <= 0.05) == TRUE])))

```
